Congestion Control

### 2017-12-13 tex/al_dente.tex

\begin{frame}{Asynchronous Actor Critic}
\begin{itemize}
\item A Deep Learning framework for reinforcement learning. Used for learning how to play video games.
\item Maximize long term reward: \begin{align*}
R_t = \left(\left(\sum_{i=0}^{k-1} \gamma^ir_{t+i}\right) + \gamma^k V(s_{t+k}; \theta_\text{v})\right),
\end{align*}
\item The \textbf{Critic} tries to estimate how much (long-term) reward one can expect considering the current state.
\end{itemize}
\end{frame}

\begin{frame}{Asynchronous Actor Critic -- Actor}
\begin{itemize}
\item The \textbf{Actor} tries to perform an action that is better than what the Critic would expect.
\item It outputs two things:
\begin{itemize}
\item What it thinks is the best action (e.g. increase the window by $0.3$)
\item A standard deviation to experiment a little bit (e.g. $0.45$)
\end{itemize}
\item So the actor outputs a normal distribution from which actions are sampled. Thanks to the standard deviation we experiment and don't get stuck with suboptimal actions. 
\end{itemize}
\end{frame}

\begin{frame}{Preliminary results -- Experiment characteristics}
\centering
\begin{tabular}{rll}
\toprule
Parameter & Value & Distribution \\
\midrule
Two-way RTT when queue is 0 & $150\,$ms & constant \\
Bottleneck bandwidth & $15\,$Mbit/s & constant \\
Number of senders & $8$ & constant \\
Flow length & $100\,$kB & exponential \\
Time between flows & $0.5\,$s & exponential \\
Simulation duration & $500\,$s & constant \\
Buffer size & $100$ packets & constant \\
Stochastic loss prob. & $0\%$ & constant \\
\bottomrule
\end{tabular}
\end{frame}

\begin{frame}{Preliminary results -- Comparison}
Stuff goes here!

@@

@@

\begin{frame}{Reward 1}
\begin{align*}
\frac{R_\text{packets}}{R_\text{duration}}\text{Sigmoid}_\alpha\left(\frac{R_\text{lost}}{R_\text{lost} + R_\text{packets}} - 0.05\right) - \frac{R_\text{lost}}{R_\text{duration}} - \frac{R_\text{delay}}{R_\text{packets}}
\end{align*}
\end{frame}

>>>>

%\begin{frame}{Asynchronous Actor Critic}
%\begin{itemize}
%\item A Deep Learning framework for reinforcement learning. Used for learning how to play video games.
%\item Maximize long term reward: \begin{align*}
%R_t = \left(\left(\sum_{i=0}^{k-1} \gamma^ir_{t+i}\right) + \gamma^k V(s_{t+k}; \theta_\text{v})\right),
%\end{align*}
%\item The \textbf{Critic} tries to estimate how much (long-term) reward one can expect considering the current state.
%\end{itemize}
%\end{frame}

\begin{frame}{Asynchronous Actor Critic}
\begin{itemize}
\item A Deep Learning framework for reinforcement learning. Used for learning how to play video games.
\item Maximize expected long term reward: \begin{align*}
R_t = \gamma r_t + (1-\gamma) R_{t+1}
\end{align*}
\item The \textbf{Critic} tries to estimate how much (long-term) reward one can expect considering the current state.
\end{itemize}
\end{frame}

\makeatletter
\begin{frame}{Exponential decay with $\gamma = 0.01$}
    \global\beamer@shrinktrue
    \gdef\beamer@shrinkframebox{
        \setbox\beamer@framebox=\vbox to\beamer@frametextheight{
            \centering
            \includegraphics[height=\beamer@frametextheight]{figures/exponential}
        }
    }
\end{frame}
\makeatother

\begin{frame}{Asynchronous Actor Critic -- How to choose $\gamma$}
\begin{itemize}
\item In literature people just set $\gamma = 0.01$. 
\item Problem: The larger the congestion window the more often we'll receive new packets!
\item $\frac{2}{k+1}$ is equivalent to a moving average considering the next $k$ elements.
\item Choose $\frac{2}{w_t+2}$ where $w_t$ is the congestion window at time step $t$.
\end{itemize}
\end{frame}

\begin{frame}{Asynchronous Actor Critic -- Actor}
\begin{itemize}
\item Wants to performs an action that are better than what the Critic would expect.
\item It outputs two things:
\begin{itemize}
\item What it thinks is the best action (e.g. increase the window by $0.3$)
\item A standard deviation to experiment a little bit (e.g. $0.45$)
\end{itemize}
\item So we get a normal distribution from which we sample.
\item Thanks to the standard deviation we experiment and don't get stuck with suboptimal actions. 
\end{itemize}
\end{frame}

@@

\makeatletter
\begin{frame}{Softplus function}
    \global\beamer@shrinktrue
    \gdef\beamer@shrinkframebox{
        \setbox\beamer@framebox=\vbox to\beamer@frametextheight{
            \centering
            \includegraphics[height=\beamer@frametextheight]{figures/softplus}
        }
    }
\end{frame}
\makeatother

\begin{frame}{Utility function}
\begin{align*}
U_t = \text{throughput} \cdot \text{Sigmoid}_\alpha\left(\text{loss rate} - 0.05 \right) - \text{sending rate}\cdot\text{loss rate}
\end{align*}
\end{frame}

\begin{frame}{Utility function}
\begin{align*}
U_t = \frac{r_{\text{received},t}}{r_{\text{duration},t}}\text{Sigmoid}_\alpha\left(\frac{r_{\text{sent},t} - r_{\text{received},t}}{r_{\text{sent},t}} - 0.05\right) - \frac{r_{\text{sent},t} - r_{\text{received},t}}{r_{\text{duration},t}}
\end{align*}
\end{frame}

\begin{frame}{Sigmoid function}
\begin{align*}
\text{Sigmoid}_\alpha(x) = \frac{1}{1+e^{\alpha (x-0.05)}}
\end{align*}
\end{frame}

\makeatletter
\begin{frame}{Sigmoid function for $\alpha = 100$ with $0.05$ cutoff}
    \global\beamer@shrinktrue
    \gdef\beamer@shrinkframebox{
        \setbox\beamer@framebox=\vbox to\beamer@frametextheight{
            \centering
            \includegraphics[height=\beamer@frametextheight]{figures/sigmoid}
        }
    }
\end{frame}
\makeatother

@@

%\begin{frame}{Preliminary results -- Experiment characteristics}
%\centering
%\begin{tabular}{rll}
%\toprule
%Parameter & Value & Distribution \\
%\midrule
%Two-way RTT when queue is 0 & $150\,$ms & constant \\
%Bottleneck bandwidth & $15\,$Mbit/s & constant \\
%Number of senders & $8$ & constant \\
%Flow length & $100\,$kB & exponential \\
%Time between flows & $0.5\,$s & exponential \\
%Simulation duration & $500\,$s & constant \\
%Buffer size & $100$ packets & constant \\
%Stochastic loss prob. & $0\%$ & constant \\
%\bottomrule
%\end{tabular}
%\end{frame}

\begin{frame}{Some data}
\includegraphics[width=\textwidth]{figures/window}
\end{frame}

\begin{frame}{Some data}
\includegraphics[width=\textwidth]{figures/score_lost}
\end{frame}

\begin{frame}{Some data}
\includegraphics[width=\textwidth]{figures/window_increase}
\end{frame}
